---
title: "R House Prices"
author: "BADS"
date: "January 15, 2017"
output: html_document
---

```{r setup,echo = FALSE ,include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sqldf)
library(devtools)
library(highcharter)
library(data.table)
library(dplyr)
library(corrplot)
library(randomForest)
library(caret)

#read the data into R

train <- fread("rf_train_x.csv")
train_original <- fread("train.csv")

#Convert Column Name for 1stFlrSf and 2ndFlrSf

colnames(train)[2] <- "firstfloorsf"
colnames(train)[3] <- "secondfloorsf"
colnames(train)[4] <- "ThirdssnPorch"

train$SalePrice <- train_original$SalePrice

train<-train[,2:ncol(train)]

```

## House Prices: Advanced Regression Techniques

Data fields


```{r check NA}

cattable <- Filter(is.character, train)

cattable <- sapply( cattable, as.factor )

colSums(is.na(cattable))

```

Potential Issue with NA in Alley, FireplaceQu, MiscFeature, Fence, PoolQC

```{r checking category distribution}

summary(cattable)

```

Utilities, GarageQual, GarageCond, Electrical, Functional, Street, PavedDrive, CentralAir, LandSlope, LandContour, Condition1, Condition2, RoofMatl, ExterCond have small distribution of catagory type

### Correlation Table (Numerical Variable)


```{r numeric, echo = FALSE}

correlationtable <- Filter(is.numeric, train)

cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
        for (j in (i + 1):n) {
            tmp <- cor.test(mat[, i], mat[, j], ...)
            p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
        }
    }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
# matrix of the p-value of the correlation
p.mat <- cor.mtest(correlationtable)

corrplot(cor(correlationtable,use = "complete.obs"), order="hclust", 
         p.mat = p.mat, sig.level = 0.01)

corrplot(cor(correlationtable,use = "complete.obs"), order="hclust", 
         p.mat = p.mat, sig.level = 0.01)

```


```{r forest, echo = FALSE}

model1 <- randomForest(SalePrice ~ .,data=train, na.action=na.omit ,mtry=3,importance=TRUE)

importance(model1,type=2)

plot(model1, log="y")

varImpPlot(model1)

check <- data.frame(train$SalePrice,model1$predicted)
colnames(check) <- c("actual","predict")

r2 <- 1 - (sum((check$actual-check$predict )^2)/sum((check$actual-mean(check$actual))^2))



```

```{r crossforest, echo = FALSE}

set.seed(998)
inTraining <- createDataPartition(train$SalePrice, p = .75, list = FALSE)

training <- train[ inTraining,]
testing  <- train[-inTraining,]

fitControl <- trainControl(## 10-fold CV
                           method = "repeatedcv",
                           number = 5,
                           repeats = 10)

rfFit1 <- train(SalePrice ~ ., data = training, 
                 method = "rf", 
                 trControl = fitControl,
                 verbose = TRUE)

```
